Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-10-30 paper/zigzag.tex
extra appendix section for interface transparency vs path length with a bit more explanation

\comment{In a realistic device the magnetic field might not be inhomogeneous, but zigzag doesn't care.}
The change in the interface transparency alone is not sufficient to explain the increase of the topological gap.
To verify this, we compute the dispersion of a system with $z_x = z_y = \SI{80}{\nm} \approx v_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
We observe that $E_\textrm{gap}$ becomes $\SI{6.1}{\mu \eV}$, a two-fold increase compared to the straight system, not the order of magnitude increase resulting from the cutting off of long trajectories.

>>>>

\section{Interface transparency vs. path length cut-off}

The zigzag geometry both increases the interface transparency (as particles typically hit the superconductoer
closer to normal incidence) as well as sets an upper limit to the trajectory length.
Here we show that the change in the interface transparency alone is not sufficient to explain the increase of the topological gap.
To verify this, we compute the dispersion of a system with $z_x = z_y = \SI{80}{\nm} \approx v_\textrm{F}$ and $W=\SI{400}{\nm}$, so that the angle of the boundaries is sufficiently large, but the boundary modulation is much smaller than the width.
We observe that $E_\textrm{gap}$ becomes $\SI{6.1}{\mu \eV}$, a two-fold increase compared to the straight system, not the order of magnitude increase resulting from the cutting off of long trajectories.
